Predictive analytics in quality assurance for assembly processes: lessons learned from a case study at an industry 4.0 demonstration cell

### 2020-11-30 02_Paper/paper.tex
Chapter 2

Based on an explorative literature review on this matter, the short outcome is that the findings that combine PA and QC are very scarce in the literature. This could be in great part, due to computer power limitations in early research and the recent increase of ML applications on this area. Related works, e.g from Krauß focused on automated machine learning for predictive quality in production \cite{krauss2020automated}; product quality prediction in a process chain \cite{krauss2019machine}; model development for predictive quality control of batch processes \cite{aumi2012model}; and ways of process modeling on quality prediction and assurance of chipboard \cite{ritter1992neue}

\AP{
       - Introduce research question
       - why do we do it?
       - what do we expect to find or prove
       - the motivation is clear

       }

>>>>

Based on an explorative literature review on this matter, the short outcome is that the findings that combine PA and QC are very scarce in the literature. This could be in great part, due to computer power limitations in early research and the recent increase of ML applications on this area. Related works, e.g from Krauß focused on automated machine learning for predictive quality in production \cite{krauss2020automated}; product quality prediction in a process chain \cite{krauss2019machine}; model development for predictive quality control of batch processes \cite{aumi2012model}; and ways of process modeling on quality prediction and assurance of chipboard \cite{ritter1992neue}. Considering the lack of literature, our goal is to decrease this gap on the research area by implementing a functional predictive model in quality assurance for an assembly process and describing the lesson learned during this implementation.
